### 2018-10-13 tex/intro.tex
Version 2.0

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{R}{ecent} years have witnessed widespread use of sophisticated frameworks such as Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. Such shuffle phase places significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs\cite{managing}.

Although continued efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in a lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stage (i.e., map task).  And the \textit{shuffle read} fetches intermediate results from \emph{remote} disks through network, which is commonly integrated as part of the tasks in descendant stage (i.e., reduce task).  Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to each of the computation task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since each phase receives a fixed bundle of resources, attaching the \emph{I/O intensive} shuffle phase to the \emph{CPU/memory intensive} computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after all the data from its ancestor stage by default. As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop\footnote{http://hadoop.apache.com/}. However, such early start is by no means a panacea. This is because although the reduce tasks can start fetching data earlier, the computation can only take place after all the data is ready. Since each phase receives a fixed bundle of resources, starting a reduce task early always introduces an unnecessary early allocation of slot.

@@

Can we efficiently optimize the data shuffling without significantly changing every framework?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.

Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle read and write from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks and pre-fetches the shuffle data to the location of the reduce tasks without launching them.
Such pre-scheduling and pre-fetching effectively desynchronize the network I/O operation, while avoiding the waste of computational resources compared to the early start mechanism.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

The workflow of DAG framework with SCache is presented in Figure \ref{fig:workflow}. SCache hijacks the intermediate data of a map task in memory space. The disk operation is skipped and the slot is released after memory copy. The in-memory intermediate data is immediately pre-fetched through network after pre-scheduling. By releasing the slot earlier and starting the network transfer ahead of reduce tasks, SCache can help the DAG framework achieve a significant performance gain. A by-product optimization of pre-scheduling is that SCache can provide a more balanced load for each node and further benefit the reduce stage by avoiding data skew.

The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks}. It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}. Unfortunately the complexity of DAG can amplify the defects of na\"{i}ve pre-scheduling schemes. In particular, randomly assign reduce tasks might result in a collision of two heavy tasks on one node. This collision can aggravate data skew, thus hurting the performance. To address this challenge, we propose a heuristic scheme to predict the shuffle output distribution and pre-schedule reduce tasks (Section \ref{opt}).

The second challenge is the \textit{in-memory data management}. To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. However, the memory is a precious resource for DAG computing. To minimize the reserved memory while maximizing the performance gain of optimization and memory utilization, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model. We use FRQ model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}

>>>>

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{R}{ecent} years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs \cite{managing}.

Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to a same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce\footnote{http://hadoop.apache.com/}. 
However, such early-start is by no means a panacea. 
This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.

@@

Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
% for the reduce tasks.
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
SCache replaces the disk operations of shuffle write by the memory copy in map tasks. 
The slot is released after the memory copy. 
The shuffle data is stored in the reserved memory of SCache until all reduce tasks are pre-scheduled. 
Then the shuffle data is pre-fetched according to the pre-scheduling results.  
The application-context-aware memory management caches the shuffle data in memory before launching the reduce task.
By applying these optimizations, SCache can help the DAG framework achieve a significant performance gain.

The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks without launching}. 
% It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}. 
First, the complexity of DAG can amplify the defects of na\"{i}ve scheduling schemes. 
In particular, randomly assigning reduce tasks might result in a collision of two heavy tasks on one node. 
This collision can aggravate data skew, thus hurting the performance. 
Second, pre-scheduling without launching violates the design of most frameworks that launch a task after scheduling.
To address the challenges, we propose a heuristic task pre-scheduling scheme with shuffle data prediction and a task co-scheduler (Section \ref{opt}).

Another challenge is the \textit{in-memory data management}. 
To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
% However, the memory is a precious resource for DAG computing. 
To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}

### 2018-10-13 tex/motivation.tex
Version 2.0

In large scale data parallel computing, shuffle is designed to achieve an all-to-all data blocks transfer among nodes. For a clear illustration, we use \textit{map tasks} to define the tasks that generate shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
% Note that one task may have both shuffle data generation and consumption in modern DAG framework. These tasks contain characteristic of both map task and reduce task. But these tasks won't change the behavior of shuffle. To avoid ambiguity, in the following paper, we will only use term of map task to represent those who produce shuffle output, and reduce task to represent those who consume shuffle output.
% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{fig/shuffle_process}
% 	\caption{Shuffle Overview}
% 	\label{fig:shuffle_process}
% \end{figure}

\textbf{Overview of shuffle process}. Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). The total number of buckets equals the number of tasks in the next step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
The partitioned shuffle output data will be spilled to local persistent storage during shuffle write.
Shuffle read starts at the beginning of reduce tasks. It fetches data as reduce input from both remote and local storage.

\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
	\label{fig:util}
\end{figure}
%In short, shuffle is loosely coupled with application context and it's I/O intensive.

\textbf{Impact of shuffle process}. Shuffle process is I/O intensive, which might introduces a significant latency to the application. Reports show that 60\% of MapReduce jobs at Yahoo!
and 20\% at Facebook are shuffle intensive workloads \cite{shufflewatcher}. For those shuffle intensive jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle intensive jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

\subsection{Observations} \label{observation}
Of course, shuffle is unavoidable in a DAG computing process. But can we mitigate or even remove the overhead of shuffle? To find the answers, we run some typical Spark applications in a 5-node EC2 cluster with \texttt{m4.xlarge}. We then measure the CPU utilization, I/O throughput, and tasks execution information of each node. Here we present the trace of one node running Spark \textit{GroupByTest} in Figure \ref{fig:util} as an example. This job has 2 rounds of tasks for each node.
We have marked the \textit{execution} phase as from the launch time of the first task to the execution finish timestamp of the last one. The \textit{shuffle write} phase is marked from the timestamp of the beginning of the first partitioned data write. The \textit{shuffle read and execution} phase is marked from the start of the first reduce launch timestamp.

% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}

\subsubsection{Coarse Granularity Resource Allocation}
In Figure \ref{fig:util}, when a slot is scheduled to a task, it will not be released until the the task completes \textit{shuffle write}. On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}. Meanwhile, shuffle is I/O intensive. Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without involving much CPU. The current coarse slot --- task mapping results in an inconsistency between resource demands and slot allocation thus decreases the resource utilization. To break this inconsistency, a finer granularity resource allocation scheme must be provided.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start \textit{shuffle read} simultaneously. The synchronized \textit{shuffle read} requests cause a burst of network traffic. As shown in Figure \ref{fig:util}, the data transfer put a great deal of stress on network bandwidth, which may results in network congestion and further hurts the performance of reduce stage.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking style I/O operation. This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in a I/O performance bounded cluster.
Besides, the legacy of spilling shuffle data to disk is too conservative in modern cluster with large memory. Compared to input dataset, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort is less than 25\% of input data. The data reported in \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. On the other hand, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory. 
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html/} 
suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ no. of nodes $\times$ no. of maximum container} per-node seem to be the right level of parallelism. Spark Configuration also recommends $2-3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}.
Since the shuffle data becomes available as soon as the end of map task execution. At the same time, the network is idle during the map stage (network utilization during map stage in Figure \ref{fig:util}). If the destination host of the shuffle data can be predicted in priori, the property of multi-round can be leveraged to overlap the \textit{shuffle read} operation.
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

Based on these observations, it is straightforward to come up with an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round DAG computing tasks, and uses memory to store the shuffle data for further decreasing shuffle overhead. To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

>>>>

In large scale data parallel computing, shuffle is designed to achieve an all-to-all data transfer among nodes. 
For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
% Note that one task may have both shuffle data generation and consumption in modern DAG framework. These tasks contain characteristic of both map task and reduce task. But these tasks won't change the behavior of shuffle. To avoid ambiguity, in the following paper, we will only use term of map task to represent those who produce shuffle output, and reduce task to represent those who consume shuffle output.
% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{fig/shuffle_process}
% 	\caption{Shuffle Overview}
% 	\label{fig:shuffle_process}
% \end{figure}

\textbf{Overview of shuffle process}. 
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduces a significant latency to the application. 
Reports show that 60\% of MapReduce jobs at Yahoo! and 20\% at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle? 
To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
A finer granularity resource allocation scheme should be provided to reduce these delays.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.

\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
Compared to input dataset, the size of shuffle data is relatively small. 
For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than 25\% of input data. 
The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as 10\%-20\%. 
On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
For a cluster with $n$ slots, the number of tasks should be $n \times k (k \geq 1)$. 
For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism. 
Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).

Since the shuffle data becomes available as soon as the end of a task's execution, 
and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data. 
To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

### 2018-10-13 tex/relatedwork.tex
Version 2.0

\section{Related Work}
This section describes related work of shuffle optimization.

@@

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is the most classic approach to handle shuffle overhead. Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, map and reduce slot ratio, etc). DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks. All of them left the explicit I/O time in an occupied computation slot. Instead, SCache can start shuffle pre-fetching without consuming slots. iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier. But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.

\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. At the same time, it achieves better data locality. Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. But all of them can not mitigate explicit I/O in both map and reduce tasks. In addition their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle in-memory caching and pre-fetching.

>>>>

\section{Related Work}

@@

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
All of them have the explicit I/O time in occupied slots. 
SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

%  by combining DAG information and heuristic algorithms.
\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. 
At the same time, it achieves better data locality. 
Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
